Untitled

### 2023-08-11 draft_v0.Rmd
Explored completion times.  From Windows.

na_interpret_affected
grid::grid.text("Fig A",x = 0.65, y=0.95, gp=grid::gpar(fontsize=20))

@@

tibble(msg = glue::glue("Missing cause for {round(x1/x*100, 2)}% of entries.")) %>% 
  kable(col.names = NULL) %>%
  kable_styling(full_width = FALSE, position = "left")

@@

dta %>% 
  group_by(directorate) %>% 
  count(name = "Nr_of_entries") %>% 
  mutate(Percentage_of_total = round(Nr_of_entries/x*100, 2)) %>% 
  arrange(desc(Nr_of_entries)) %>% 
  kable(title = "Number and percentage of entries per Directorate") %>%
  kable_styling(full_width = FALSE, position = "left")

@@

>>>>

na_interpret_affected
grid::grid.text("Fig. A",x = 0.65, y=0.95, gp=grid::gpar(fontsize=20))

@@

tibble(msg = glue::glue("Missing cause for {round(x1/x*100, 2)}% of Urban Mobility entries.")) %>% 
  kable(col.names = NULL) %>%
  kable_styling(full_width = FALSE, position = "left")

@@

dta %>% 
  group_by(directorate) %>% 
  count(name = "Nr_of_entries") %>% 
  mutate(Percentage_of_total = round(Nr_of_entries/x*100, 2)) %>% 
  arrange(desc(Nr_of_entries)) %>% 
  rename(Directorate = directorate) %>% 
  kable(title = "Number and percentage of entries per Directorate") %>%
  kable_styling(full_width = FALSE, position = "left")

@@

# completion time missing
x <- nrow(dta_um)

dta_um %>% 
  group_by(is.na(completion_timestamp)) %>% 
  count(name = "Nr_missing") %>% 
  ungroup() %>% 
  rename(Missing_completion_time = 1) %>% 
  mutate(across(Missing_completion_time, ~ifelse(.x == TRUE, "yes", "no")),
         Percentage = round(Nr_missing/x*100, 2)) %>% 
  kable() %>%
  kable_styling(full_width = FALSE, position = "left")

# breakdown of entries with missing completion times

x <- c("department", "branch", "section", "code_group",
  "code", "cause_code_group", "cause_code", "official_suburb")

tmp <- map(x, 
    ~dta_um %>% 
  filter(is.na(completion_timestamp)) %>% 
  select(notification_number, all_of(.x)) %>% 
  mutate(across(-notification_number, ~paste(cur_column(), .x, sep = ":")),
         value = 1) %>% 
    rename(key = 2) %>% 
  pivot_wider(names_from = key, values_from = value)) %>% 
  purrr::reduce(inner_join) %>% 
  as.data.frame()

tmp[is.na(tmp)] <- 0

UpSetR::upset(tmp)

# exclude data with no completion time

dta_um <- dta_um %>% 
  filter(!is.na(completion_timestamp))

plotdta <- dta_um %>% 
  mutate(diff_time_hrs = as.integer(completion_timestamp - creation_timestamp)/60) %>% 
  select(notification_number, diff_time_hrs, code_group, code, cause_code_group,
         cause_code, official_suburb)

plot_time_per_var <- function(dataset = plotdta, column = "code_group", hours_cutoff = 96){

  x <- which(names(dataset) == column)
  dataset <- dataset %>% 
    rename(col_select = x)

  tmp <- dataset %>% 
  group_by(col_select) %>% 
  summarise(n = n(),
            med_hrs = median(diff_time_hrs),
            q5 = quantile(diff_time_hrs, probs = 0.05),
            q80 = quantile(diff_time_hrs, probs = 0.8),
            q95 = quantile(diff_time_hrs, probs = 0.95)) %>% 
  ungroup()

p1 <- tmp %>% 
  filter(q95 < hours_cutoff) %>% 
  select(col_select) %>% 
  inner_join(dataset %>% 
               select(col_select, diff_time_hrs)) %>% 
  ggplot(aes(diff_time_hrs, col_select))+
  ggdist::stat_interval()+
  labs(y = column)

p2 <- tmp %>% 
  filter(q5 >= hours_cutoff) %>% 
  select(col_select) %>% 
  inner_join(dataset) %>% 
  mutate(time_weeks = (diff_time_hrs/24)/7) %>% 
  ggplot(aes(time_weeks, col_select))+
  ggdist::stat_interval()+
  labs(y = column)

return(list(hours = p1, weeks = p2))

}

plotlist <- plot_time_per_var(dataset = plotdta, column = "code_group", hours_cutoff = 96)

ggpubr::ggarrange(plotlist = plotlist)

plotlist <- plot_time_per_var(dataset = plotdta, column = "code", hours_cutoff = 96)

ggpubr::ggarrange(plotlist = plotlist)

plotlist <- plot_time_per_var(dataset = plotdta, column = "cause_code_group", hours_cutoff = 96)

ggpubr::ggarrange(plotlist = plotlist)

plotlist <- plot_time_per_var(dataset = plotdta, column = "cause_code", hours_cutoff = 96)

ggpubr::ggarrange(plotlist = plotlist)

plotdta %>% 
  ggplot(aes(diff_time_hrs, official_suburb))+
  ggdist::stat_interval()

ggpubr::ggarrange(plotlist = plotlist)
